The Functional Therapeutic Chemical Classification System

### 2013-10-10 document.tex
core article revised

The FTC is a novel classification for approved drugs, which can be used as a starting point to 
generate drug repurposing hypotheses. We have guided the reader through some of the ways the resource 
can be explored. No experimental validations have been presented in this manuscript, yet references to 
supporting literature was provided in order to legitimate the claims. The main goal of this document is to 
introduce the resource to the community; deeper analyses are being performed over the classification at the time of writing.
This classification leverages the information present in various databases and ontologies, similarly to the 
Open PHACTS initiative \citep{williams2012open} and to the work done by \cite{hoehndorf2012identifying}. The FTC
mostly differentiates itself from these projects by providing a whole new set of novel categories, 
dedicated to tackle a very specific problem: drug repositioning.

>>>>

The FTC is a novel classification for approved drugs, which can be used as a starting point to 
generate drug repurposing hypotheses. We have guided the reader through some of the ways the resource 
can be explored. No experimental validations have been presented in this manuscript, yet references to 
supporting literature was provided in order to legitimate the claims. The main goal of this document is to 
introduce the resource to the community; deeper analyses are being performed over the classification at the time of writing.
This classification leverages the information present in various databases and ontologies, similarly to the 
Open PHACTS initiative \citep{williams2012open} and to the work done by \cite{hoehndorf2012identifying}. The FTC
mostly differentiates itself from these projects by providing a whole set of new categories on the top of the integrated
information, dedicated to tackle a very specific problem: drug repositioning.
